%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV of Tapan Nallan
% LaTeX Template
% Version 2.0 (26/10/2017)
% 
% https://github.com/tapanchandra/my-resume
% 
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% The Original template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Tapan Nallan} % Your name
\cvjobtitle{Senior Java Developer} % Job title/career 
\cvnumberphone{+49 1794231577} % Phone number
\cvsite{http://www.tapanchandra.com} % Personal website
\cvmail{tapanc.nallan@gmail.com} % Email address
\cvgithub{https://github.com/tapanchandra} % Github profile
\cvbitbucket{} % Bitbucket profile
\cvstackoverflow{} % Stackoverflow profile
\cvlinkedin{https://goo.gl/DPauU1} % LinkedIn profile
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

\education{
	{Masters in Information Technology/IIIT, Hyderabad, India/2010-2012},
	{B.Tech in Computer Science/JNTU, Hyderabad, India/2004-2008},
	{Highschool, Board of Intermediate Education/Sri Chaithanya, Hyderabad, India/2001-2003},
	{Xth, CBSE/Atomic Energy Central School,/1999-2001},
} 

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\sklanguages{{Golang/2},{Python 3/4},{Kotlin/3},{Java 8/4}}
\skplatformsntools{{Docker, Kubernetes/2},{AWS/2},{CI With Jenkins/3},{Angular,VueJS/3},{Spring Platform/4}} 
%------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 PROFILE
%----------------------------------------------------------------------------------------
\begingroup
\vspace{-10 pt}
\section{Profile}
\setlength{\parindent}{1cm}\linebreak\indent{
	A decade long career in software development has only increased my appetite for bigger and more rewarding challenges. I have worked as a full stack developer with experience in all aspects of development. My core strengths are as a Java/Kotlin developer working with spring platform on the backend and VueJS on the frontend.
}
\endgroup

\vspace{10 pt}

\section{Summary}
\begin{itemize}[leftmargin=*]
	\item[$\checkmark$] 15 years experience in enterprise software development.
	\item[$\checkmark$] Worked extensively with the tools and frameworks in Spring platform.
	\item[$\checkmark$] Experienced in JVM languages including Java, Kotlin, Groovy etc.
	\item[$\checkmark$] Worked with Relational DB like MySQl, OracleDB etc.. as well as NoSql Databases such as Elastic search.
	\item[$\checkmark$] Good Knowledge of Docker and Kubernetes.
	\item[$\checkmark$] Fairly Knowledgeable in frontend with experience in Angular and VueJS
	\item[$\checkmark$] Experience in Profiling and performance testing JVM applications
	\item[$\checkmark$] Experience in developing Continuous Integration Workflows using Jenkins.
	\item[$\checkmark$] Beginner Knowledge in AWS as a developer
	\item[$\checkmark$] Always eager to learn new technologies and architectures
	\item[$\checkmark$] Permanent residency visa in germany.
\end{itemize}

\vspace{10 pt}

\section{Experience} 
 
\begin{twenty} % Environment for a list with descriptions
	\twentyitem{Verimi GmbH}{https://verimi.de/kontakt/}{Dec 2018 $-$ Present}{4 Years}{
		
		\begin{itemize}[leftmargin=*]
			\item Large Microservices backend system handling millions of logins and transactions
   			\item A Complex Oauth2 Open ID connect server 
			\item Developed with spring boot 3 and Java 17
		\end{itemize}	
	}
	\twentyitem{Invia Flights GmbH}{https://www.invia.de/}{May 2018 $-$ Dec 2018}{6 Months}{
		
		\begin{itemize}[leftmargin=*]
			\item Worked on a Fraud prevention application
			\item Developed with spring boot with kotlin, with a VueJS frontend.
		\end{itemize}	
	}

	\twentyitem{JDA Software}{www.jda.com}{Jul 2012 $-$ April 2018}{5 Years 10 Months}{
		
		\begin{itemize}[leftmargin=*]
			\item Worked on multiple projects developing various supply chain applications
			\item Primarily used Java with Spring as well as other integration frameworks such as Camel, Kafka, activemq etc.
		\end{itemize}	
	}

	\twentyitem{Siemens $-$ SISL}{www.siemens.co.in}{Jan 2012 $-$ Jun 2012}{6 Months}{
		
		\begin{itemize}[leftmargin=*]
			\item Interned at Siemen's Software division in Bangalore
			\item Worked on a research project designing static code rulesets for fxcop
		\end{itemize}	
	}

	\twentyitem{EBT Pvt Ltd}{www.ebtech.biz}{Aug 2009 $-$ July 2010}{11 Months}{
		
		\begin{itemize}[leftmargin=*]
			\item Developed Java servlets based web applications for procurement handling for a mid size client.
		\end{itemize}	
	}

	\twentyitem{Chrysalis Information Systems}{www.cislworld.com}{Aug 2008 $-$ Aug 2009}{1 Year}{
		
		\begin{itemize}[leftmargin=*]
			\item Developed business process applications for a translation company using Java and .NET.
			\item Worked on development, testing and deployment of the applications for the client on site.
		\end{itemize}	
	} 

	\twentyitem{Orange Technologies Pvt Ltd}{}{Nov 2007 $-$ April 2008}{6 Months}{
		
		\begin{itemize}[leftmargin=*]
			\item Worked as a Software Intern
			\item Attended trainings on Java and web technologies
			\item Worked on a Wedding Website creator application developed with PHP in the front-end and a xml based soap backend developed in Java
		\end{itemize}	
	}
\end{twenty}

\section{Other Skills}

\maketag{Apache Camel} \maketag{MuleSoft Platform} \maketag{Nifi} \maketag{OSGI with Karaf} \maketag{ActiveMQ} \maketag{Bladelogic} \maketag{Playframework} \maketag{Nodejs} \maketag{Python Django}
\maketag{PHP CodeIgniter} \maketag{Android}
\end{document} 
